Misperceptions Regarding Women's Employment Outside the Home and Their Impact on Women in Saudi Arabia

### 2024-02-14 outputs/paper/paper.qmd
data cleaning is included now

>>>>

## Data cleaning
The raw dataset underwent a cleaning process to address missing values and recalibrate variables. This included updating the labor_demand_guess from multiple sources if it was missing, recalculating signed_up_number based on specific conditions, and removing out-of-range values from the age. New variables like college_deg and married were generated based on education and marital status, respectively. The dataset also saw the introduction of proportionate variables such as num_know_per and num_mfs_per. After refining variables for analysis, such as outside_guess, semiseg_guess, and mwage_guess, and their associated calculations, irrelevant variables were dropped. The cleaned data was then saved and is now ready for further analysis.
